\clearpage

\section{White Noise}

\begin{tcolorbox}	
	\begin{tabular}{p{2.75cm} p{0.2cm} p{10.5cm}} 	
		\textbf{Header File}   &:& white\_noise\_20180420.h \\
		\textbf{Source File}   &:& white\_noise\_20180420.cpp \\
	\end{tabular}
\end{tcolorbox}

\maketitle
This block generates a gaussian pseudo-random noise signal with a given spectral density. It can be initialized with three different seeding methods to allow control over correlation and reproducibility:

\begin{enumerate}
	\item DefaultDeterministic
	\item RandomDevice
	\item Selected
\end{enumerate}

This block does not accept any input signal. It produces can produce a real or complex output, depending on the used output signal.

\subsection*{Input Parameters}

\begin{table}[h]
	\centering
	\begin{tabular}{|c|c|c|c|c}
		\cline{1-4}
		\textbf{Parameter} & \textbf{Type} &\textbf{Values} &   \textbf{Default}& \\ \cline{1-4}
		seedType 		 & enum 	& DefaultDeterministic, RandomDevice, Selected & RandomDevice \\ \cline{1-4}
		spectralDensity  & real 	& > 0  			& $1.5\times10^{-17}$ \\ \cline{1-4}
		seed 	   		 & int 		& $\in$ [1, $2^{32}-1$] 	& 1 \\ \cline{1-4}
		samplingPeriod	 & double 	& > 0 & 1.0 \\ \cline{1-4} \cline{1-4}
	\end{tabular}
	\caption{White noise input parameters}
	\label{table:noise_in_par}
\end{table}

\subsection*{Methods}

WhiteNoise(vector<Signal *> \&InputSig, vector<Signal *> \&OutputSig) :Block(InputSig, OutputSig){};
\bigbreak	
void initialize(void);
\bigbreak
bool runBlock(void);
\bigbreak
void setNoiseSpectralDensity(double SpectralDensity) { spectralDensity = SpectralDensity; }
\bigbreak
double const getNoiseSpectralDensity(void){ return spectralDensity; }
\bigbreak
void setSeedType(SeedType sType){ seedType = sType; };
\bigbreak
SeedType const getSeedType(void){ return seedType; };
\bigbreak
void setSeed(int newSeed) { seed = newSeed; }
\bigbreak
int getSeed(void){ return seed; }

\subsection*{Functional description}

The \textit{seedType} parameter allows the user to select between one of the three seeding methods to initialize the pseudo-random number generators (PRNGs) responsible for generating the noise signal.


\textbf{DefaultDeterministic}: Uses default seeds to initialize the PRNGs. These are different for all generators used within the same block, but remain the same for sequential runs or different \textit{white\_noise} blocks. Therefore, if more than one \textit{white\_noise} block is used, another seeding method should be chosen to avoid producing the exact same noise signal in all sources.

\textbf{RandomDevice}: Uses randomly chosen seeds using \textit{std::random\_device} to initialize the PRNGs.

\textbf{SingleSelected}: Uses one user selected seed to initialize the PRNGs. The selected seed is passed through the variable \textit{seed}. If more than one generator is used, additional seeds are created by choosing the next sequential integers. For instance, if the user selected seed is $10$, and all the four PRNGs are used, the used seeds will be $[10, 11, 12, 13]$.

The noise is obtained from a gaussian distribution with zero mean and a given variance. The variance is equal to the noise power, which can be calculated from the spectral density $n_0$ and the signal's bandwidth $B$, where the bandwidth is obtained from the defined sampling time $T$.

\begin{equation}
N = n_0 B = n_0 \frac{2}{T}
\end{equation}

If the signal is complex, the noise is calculated independently for the real and imaginary parts, and the spectral density value is divided by two, to account for the two-sided noise spectral density.


%\subparagraph*{AllSelected}
%Uses user selected seeds to initialize the PRNGs. The selected seed is passed through the variable \textit{seed}. If more than one generator is used, additional seeds are created by choosing the next sequential integers.

\subsection*{Input Signals}


\subparagraph*{Number:} 0

\subsection*{Output Signals}

\subparagraph*{Number:} 1 or more

\subparagraph*{Type:} RealValue, ComplexValue or ComplexValueXY

\subsection*{Examples}

\paragraph*{Random Mode}

\subsection*{Suggestions for future improvement}
